---
title: "Instance results"
output:
  html_document:
    self_contained: yes
    theme: united
    highlight: tango
    # df_print: paged
    # code_folding: show
    toc: true
    toc_float: true
    number_sections: true
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, encoding) { 
    out_dir <- here::here("docs/");
    rmarkdown::render(inputFile,
                      encoding=encoding, 
                      output_file=file.path(out_dir, 'results.html')) })
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
here::i_am("results/results.Rmd")  # specify relative path given project
# remotes::install_github("relund/gMOIP")
# remotes::install_github("fischuu/OjaNP")
# library(gMOIP)
library(DT)
library(tidyverse)
# library(knitr)
# library(rgl)
# rgl::setupKnitr()
# options(rgl.useNULL=TRUE)
# rgl::par3d("family" = "serif")
conflicted::conflicts_prefer(plotly::layout)
conflicted::conflicts_prefer(dplyr::filter)
knitr::opts_chunk$set(
  echo = FALSE,
  message=FALSE, include = TRUE, warning = FALSE,
  out.width = "99%", fig.width = 12, fig.align = "center", fig.asp = 0.8
)
```

This report contains different plots and tables that may be relevant for analyzing the results. Given a problem consisting of $m$ subproblems with $Y_N^s$ given for each subproblem $s$, we use a filtering algorithm to find $Y_N$. 

The following instance/problem groups are generated given:

  * $p=2,\ldots, 5$. 
  * $S=2,\ldots 5$ where $S$ is the number of subproblems. 
  * All subproblems have the same method config or half have method `u` and `l`.
  * Five instances for each config. 

```{r}
datFull <- read_csv(here::here("results/results.csv"))
```


`r nrow(datFull)` problems have been solved.

```{r}
# remove results where have not solved all instances
dat <- datFull |> 
  rename(S = m) |> 
  mutate(spCard = spAveCard, method = toupper(method)) |> 
  group_by(p, S, method, spCard1) %>% 
  filter(n() == 5) %>% 
  ungroup() #|> view()
```

## Size of $Y_N$

What is $|Y_N|$ given the different methods of generating the set of nondominated points for the subproblems?

```{r}
dat %>% 
  ggplot(aes(x = spCard, y = card, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ S, scales = "free", labeller =  "label_both")  + 
  labs(title = "Number of nondominated points given subproblem cardinality",
       y = "Cardinality Y_N",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = spCard, y = card, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_wrap(p ~ S, scales = "free", labeller =  "label_both")  + 
  labs(title = "Number of nondominated points given subproblem cardinality",
       y = "Cardinality Y_N",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = spCard, y = card, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ S, scales = "free_y", labeller = "label_both")  + 
  labs(title = "Number of nondominated points given subproblem cardinality (log2) scale",
       y = "Cardinality Y_N",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") +
  scale_y_continuous(trans = "log2")
```


```{r}
dat %>% 
  ggplot(aes(x = p, y = card, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(S ~ spCard, scales = "free_y", labeller =  "label_both")  + 
  labs(title = "Number of nondominated points given subproblem cardinality",
       y = "Cardinality Y_N",
       x = "p",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = S, y = card, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ spCard, scales = "free_y", labeller =  "label_both")  + 
  labs(title = "Number of nondominated points given subproblem cardinality",
       y = "Cardinality Y_N",
       x = "S",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>%
  ggplot(aes(x = spCard, y = card, color = factor(p))) +
  geom_point() +
  stat_summary(fun="mean", geom="line") +
  facet_wrap(vars(method), scales = "free", labeller = "label_both")  +
  labs(title = "Number of nondominated points given subproblem cardinality",
       y = "Cardinality Y_N",
       x = "Subproblem cardinality",
       color = "p") +
  theme(legend.position = "bottom")
```

```{r}
dat %>% 
  ggplot(aes(x = spAvePctExt, y = card, color = factor(spCard), shape = method, group = method)) +
    stat_summary(fun="mean", geom="line", color = "gray70") +
    # stat_summary(aes(group = factor(spCard), color = factor(spCard)), fun="mean", geom="line", size = 0.05) +
    geom_point() + 
    facet_grid(p ~ S, scales = "free_y", labeller =  "label_both")  + 
    labs(title = "Number of nondominated points",
       y = "Cardinality Y_N",
       x = "Ave relative number of subproblem extreme",
       color = "Subproblem cardinality") +
  theme(legend.position = "bottom") 
```


### Summary tables

Below summary tables with summary results for different aggregation levels are given (`card = |Y_N|`).

```{r}
dat %>% 
  group_by(method) %>% 
  summarise(min_card = min(card), mean_card = mean(card), max_card = max(card), instances = n()) |> 
  DT::datatable()
```

```{r}
dat %>% 
  group_by(method, S, p) %>% 
  summarise(min_card = min(card), mean_card = mean(card), max_card = max(card), instances = n()) |> 
  DT::datatable()
```

```{r}
dat %>% 
  group_by(method, S, p, spCard) %>% 
  summarise(min_card = min(card), mean_card = mean(card), max_card = max(card), instances = n()) |> 
  DT::datatable()
```

### Regression fit

Let us try to fit the results using function $y=c_1 s^{(c_2p)} S^{c_3p}$ (different functions was tried and this gave the highest $R^2$) for each method:

```{r}
# Fit exponential regression model
library(tidymodels)
tidymodels_prefer()
lm_spec <- linear_reg()
# lm_fit <- fit(lm_spec, log(card) ~ -1 + method + method:I(p * log(spCard)) + method:I(p * log(S)) + I(log(spCard)), data = dat)
# summary(lm_fit)
# tidy(lm_fit)

regressions <- 
  dat %>%
  nest(data = c(-method)) %>% 
  mutate(
    fit = map(data, ~ lm(log(card) ~ I(p * log(spCard)) + I(p * log(S)), data = .x)),
    tidied = map(fit, tidy),
    glanced = map(fit, glance)
  )

regressions %>% 
  select(-data) |> 
  unnest(glanced)

# test <- function(p, spCard, S) {
#   regressions |> 
#     mutate(p1 = map_dbl(fit, function(x) exp(predict(x, newdata = tibble(spCard = spCard, S = S, p = p,))))) |> 
#     mutate(p2 = map_dbl(tidied, function(x) exp(x$estimate[1]) * spCard^(x$estimate[2] * p) * S^(x$estimate[3] * p)))
#   # cf <- coef |> filter(method == "u") |> select(-method) |> unlist()
#   # return(cf[1] * spCard^(cf[2] * p) * S^(cf[3] * p))
# }
# test(p = 3, spCard = 200, S = 3)

coef <- regressions %>% 
  select(-data) |> 
  unnest(tidied) |> 
  mutate(estimate = if_else(term == "(Intercept)", exp(estimate), estimate),
         coef = rep(c("c1", "c2", "c3"), 4)) |> 
  select(method, coef, estimate) |> 
  pivot_wider(names_from = coef, values_from = estimate)
coef

# model <- lm(log(card) ~ -1 + method + method:I(p * log(spCard)) + method:I(p * log(S)), data = dat)
# summary(model)
# par(mfrow=c(2,2))
# plot(model)
```

The parameters estimates are:

```{r}
model <- lm(log(card) ~ -1 + method + method:I(p * log(spCard)) + method:I(p * log(S)), data = dat)
# some plots
library(plotly)
spCard <- seq(100, 300, by = 10)
S <- 1:5
p <- 3
method <- factor("L", levels = unique(dat$method))
card <- t(outer(spCard, S, function(spCard, S) exp(predict(model, newdata = tibble(spCard = spCard, S = S, p = p, method = method)))))
dat1 <- expand_grid(S = S, p = p, spCard = spCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- plot_ly() %>%
  add_surface(x = spCard, y = S, z = card,
    contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), colorscale = "Viridis", opacity = 0.8)
  # add_trace(type = 'scatter3d',
  #           mode = 'markers',
  #           data = dat1,
  #           x = ~spCard, y = ~S, z = ~card,
  #           marker = list(color = 'red', size = 5, symbol = 'circle'))

method <- factor("S", levels = unique(dat$method))
card <- t(outer(spCard, S, function(spCard, S) exp(predict(model, newdata = tibble(spCard = spCard, S = S, p = p, method = method)))))
dat1 <- expand_grid(S = S, p = p, spCard = spCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- fig |> add_surface(x = spCard, y = S, z = card,
  contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), colorscale = 'Rainbow', opacity = 1)

method <- factor("ul", levels = unique(dat$method))
card <- t(outer(spCard, S, function(spCard, S) exp(predict(model, newdata = tibble(spCard = spCard, S = S, p = p, method = method)))))
dat1 <- expand_grid(S = S, p = p, spCard = spCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- fig |> add_surface(x = spCard, y = S, z = card,
  contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), colorscale = 'heat', opacity = 1)

method <- factor("u", levels = unique(dat$method))
card <- t(outer(spCard, S, function(spCard, S) exp(predict(model, newdata = tibble(spCard = spCard, S = S, p = p, method = method)))))
dat1 <- expand_grid(S = S, p = p, spCard = spCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- fig |> add_surface(x = spCard, y = S, z = card,
  contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), colorscale = 'Cividis', opacity = 1) |> 
  layout(
    title = list(
      x = 0.5, y = 0.9, z = 0.9, xanchor = "center",
      text = "Y_N for p = 3 and method u, S, ul and l (higest Y_N)"  # Title text
    ),
    scene = list(
    xaxis = list(range = range(spCard)),  # Set x-axis limits
    yaxis = list(range = range(S),  # Set y-axis limits
    zaxis = list(range = range(card))     # Set z-axis limits
  ))) 

fig
```



```{r}
spCard <- seq(100, 300, by = 10)
S <- 1:5
p <- 4
method <- factor("M", levels = unique(dat$method))
card <- t(outer(spCard, S, function(spCard, S) exp(predict(model, newdata = tibble(spCard = spCard, S = S, p = p, method = method)))))
dat1 <- expand_grid(S = S, p = p, spCard = spCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- plot_ly() %>%
  add_surface(x = spCard, y = S, z = card,
    contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), opacity = 0.8)

p <- 3
card <- t(outer(spCard, S, function(spCard, S) exp(predict(model, newdata = tibble(spCard = spCard, S = S, p = p, method = method)))))
dat1 <- expand_grid(S = S, p = p, spCard = spCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig <- fig |> add_surface(x = spCard, y = S, z = card,
  contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), opacity = 0.8) 

p <- 2
card <- t(outer(spCard, S, function(spCard, S) exp(predict(model, newdata = tibble(spCard = spCard, S = S, p = p, method = method)))))
dat1 <- expand_grid(S = S, p = p, spCard = spCard, method = method)
dat1 <- bind_cols(dat1, card = exp(predict(model, newdata = dat1)))
fig |> add_surface(x = spCard, y = S, z = card,
  contours = list(
    x = list(show = TRUE, color = 'lightgray', width = 2),
    y = list(show = TRUE, color = 'lightgray', width = 2),
    z = list(show = TRUE, color = 'lightgray', width = 2)
  ), opacity = 0.8) |> 
  layout(
    title = list(
      x = 0.5, y = 0.9, z = 0.9, xanchor = "center",
      text = "Y_N for p = 2-4 and method"  # Title text
    ),
    scene = list(
    xaxis = list(range = range(spCard)),  # Set x-axis limits
    yaxis = list(range = range(S),  # Set y-axis limits
    zaxis = list(range = range(card))     # Set z-axis limits
  ))) 
```




## Relative size of $Y_N$

```{r}
dat %>% 
  ggplot(aes(x = spCard, y = card / ubCard, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ S, labeller = "label_both")  + 
  labs(title = "Relative size of nondominated points compared to total enumeration given subproblem cardinality",
       y = "Cardinality Y_N",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r, eval=FALSE}
dat %>% 
  ggplot(aes(x = spCard, y = card / ubCard, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ S, labeller = "label_both")  + 
  labs(title = "Relative size of nondominated points compared to total enumeration given subproblem cardinality (log2 scale)",
       y = "Cardinality Y_N",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") +
  scale_y_continuous(trans = "log2")
```

```{r}
dat %>% 
  ggplot(aes(y = card / ubCard, x = method, color = method)) +
  geom_boxplot() +
  facet_grid(p ~ S, labeller = label_both) +
  labs(title = "Relative size of nondominated points compared to total enumeration",
       y = "%",
       x = "Method",
       color = "Method(s) used to generate subproblems") +
  theme(legend.position = "bottom")
```


```{r, eval=FALSE}
dat %>% 
  ggplot(aes(y = card / ubCard, x = method, color = method)) +
  geom_boxplot() +
  facet_grid(S ~ p, labeller = label_both) +
  labs(title = "Relative size of nondominated points compared to total enumeration (log2 scale)",
       y = "%",
       x = "Method",
       color = "Method(s) used to generate subproblems") +
  theme(legend.position = "bottom") +
  scale_y_continuous(trans = "log2")
```


<!-- ```{r} -->
<!-- dat %>%  -->
<!--   ggplot(aes(y = card / points_hypercube, x = method, color = method)) + -->
<!--   geom_boxplot() + -->
<!--   facet_grid(S ~ p, margins = T, labeller = label_both) + -->
<!--   labs(title = "Relative size of nondominated points compared to total enumeration", -->
<!--        y = "%", -->
<!--        x = "Method", -->
<!--        color = "Method(s) used to generate subproblems") + -->
<!--   theme(legend.position = "bottom") -->
<!-- ``` -->


## Nondominated points classification

We classify the nondominated points into, extreme, supported non-extreme and unsupported.

```{r}
dat %>% 
  ggplot(aes(x = spCard, y = pctExt, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ S, margins = T, labeller = label_both)  + 
  labs(title = "Relativ number of extreme points given subproblem cardinality",
       y = "%",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = p, y = pctExt, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(spCard ~ S, margins = T, labeller = label_both)  + 
  labs(title = "Relativ number of extreme points given subproblem cardinality",
       y = "%",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = S, y = pctExt, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ spCard, margins = T, labeller = label_both)  + 
  labs(title = "Relativ number of extreme points given subproblem cardinality",
       y = "%",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = spCard, y = pctSup, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ S, margins = T, labeller = label_both)  + 
  labs(title = "Relativ number of supported points given subproblem cardinality",
       y = "%",
       x = "Subproblem cardinality",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom") 
```

```{r}
dat %>% 
  ggplot(aes(x = method, y = pctExt, color = method)) +
  geom_boxplot() + 
  facet_grid(p ~ S, margins = T, labeller = label_both) +
  labs(title = "Relativ number of extreme points given method",
       y = "%",
       x = "Method",
       color = "Methods used to generate subproblems") +
  theme(legend.position = "bottom")
```

```{r}
dat %>% 
  ggplot(aes(x = spAvePctExt, y = pctExt, color = method)) +
  geom_point() + 
  facet_grid(p ~ S, margins = T, labeller = label_both) +
  labs(title = "Relativ number of extreme points",
       y = "% extreme master",
       x = "Avg. % extreme subproblems",
       color = "Method(s) used to generate subproblems") +
  theme(legend.position = "bottom")
```


```{r}
dat %>% 
  ggplot(aes(x = spAvePctExt, y = pctExt, color = factor(spCard), shape = method)) +
  geom_point() + 
  facet_grid(p ~ S, margins = T, labeller = label_both) +
  labs(title = "Relativ number of extreme points",
       y = "% extreme master",
       x = "Avg. % extreme subproblems",
       color = "Subproblem cardinality") +
  theme(legend.position = "bottom")
```


```{r}
dat %>% 
  ggplot(aes(y = pctExt/spAvePctExt, x = spCard, color = method)) +
  geom_point() + 
  stat_summary(fun="mean", geom="line") +
  facet_grid(p ~ S, margins = T, labeller = label_both) +
  labs(title = "Relativ: % extreme master / % extreme subproblems",
       y = "% extreme master / % extreme subproblems",
       x = "Subproblem cardinality",
       color = "Method(s) used to generate subproblems") +
  theme(legend.position = "bottom")
```

### Summary tables

Below summary tables with summary results for different aggregation levels are given. Only instances which have been classified are included.

```{r}
dat %>% 
  filter(!is.na(extreme), !is.na(supported), !is.na(unsupported)) |> 
  group_by(p, S, method, spCard) %>% 
  filter(n() == 5) %>% 
  group_by(method) %>% 
  summarise(mean_card = mean(card), 
            mean_sup = mean(supported),
            mean_pctSup = mean(pctSup),
            mean_ext = mean(extreme), 
            mean_pctExt = mean(pctExt),
            mean_unsup = mean(unsupported), 
            instances = n()) |> 
  mutate(across(where(is.numeric), round, digits = 2)) |> 
  DT::datatable() 
```

```{r}
dat %>% 
  filter(!is.na(extreme), !is.na(supported), !is.na(unsupported)) |> 
  group_by(p, S, method, spCard) %>% 
  filter(n() == 5) %>% 
  group_by(method, S, p) %>% 
  summarise(mean_card = mean(card), 
            mean_sup = mean(supported),
            mean_pctSup = mean(pctSup),
            mean_ext = mean(extreme), 
            mean_pctExt = mean(pctExt),
            mean_unsup = mean(unsupported), 
            instances = n()) |> 
  mutate(across(where(is.numeric), round, digits = 2)) |> 
  DT::datatable() 
```

```{r}
dat %>% 
  filter(!is.na(extreme), !is.na(supported), !is.na(unsupported)) |> 
  group_by(p, S, method, spCard) %>% 
  filter(n() == 5) %>% 
  group_by(method, S, p, spCard) %>% 
  summarise(mean_card = mean(card), 
            mean_sup = mean(supported),
            mean_pctSup = mean(pctSup),
            mean_ext = mean(extreme), 
            mean_pctExt = mean(pctExt),
            mean_unsup = mean(unsupported), 
            instances = n()) |> 
  mutate(across(where(is.numeric), round, digits = 2)) |> 
  DT::datatable() 
```

Relative number of extreme (min and max included):

```{r}
dat |> 
  summarise(minPctEx = min(pctExt, na.rm = T), avePctExt = mean(pctExt, na.rm = T), maxPctEx = max(pctExt, na.rm = T)) 

dat |> 
  group_by(method) |> 
  summarise(minPctEx = min(pctExt, na.rm = T), avePctExt = mean(pctExt, na.rm = T), maxPctEx = max(pctExt, na.rm = T)) |> 
  arrange(desc(avePctExt))
```





## Problems solved for the analysis  



```{r, out.width = "100%"}
DT::datatable(dat, width = "100%", options = list(autoWidth = T, scrollX = TRUE, columnDefs = list(list(width = '250px', targets = c(1)))))
```

## Generator sets - Summary tables

```{r}
dat_MGS <- read_csv(here::here("results/results_minimum_generator_sets.csv")) # |> view()

# rename path so it matches format of dat
dat_MGS <- dat_MGS %>% mutate(path = str_replace(filename, 'prob-','alg1-prob-' ))

# merge, adding the columns to dat_MGS
dat_MGS <- right_join(dat, dat_MGS)

decimals <- 1 / (10^1) # for percent

dat_MGS <- dat_MGS |> 
  transmute(path, method, S, p, sp_card = spCard, 
            mgs_card_vec = str_replace(MGS_sizes, "-", "|"),
            mean_mgs_card = MGS_size/S, 
            pct_mgs_card = MGS_size/max_size,  
            card, supported, pct_sup = pctSup, 
            extreme, pct_ext = pctExt, unsupported, 
            cpu = running_time)
```

Below summary tables with summary results for different aggregation levels are given.

```{r}
dat_MGS %>% 
  group_by(method) %>% 
  summarise(mean_mgs_card = mean(mean_mgs_card),
            mean_pct_mgs_card = mean(pct_mgs_card),
            mean_cpu = mean(cpu),
            instances = n()) |> 
  mutate(across(where(is.numeric), round, digits = 2)) |> 
  DT::datatable() 
```

```{r}
dat_MGS %>% 
  group_by(method, S, p) %>% 
  summarise(mean_mgs_card = mean(mean_mgs_card),
            mean_pct_mgs_card = mean(pct_mgs_card),
            mean_cpu = mean(cpu),
            instances = n()) |> 
  mutate(across(where(is.numeric), round, digits = 2)) |> 
  DT::datatable() 
```

```{r}
dat_MGS %>% 
  group_by(method, S, p, sp_card) %>% 
  summarise(mean_mgs_card = mean(mean_mgs_card),
            mean_pct_mgs_card = mean(pct_mgs_card),
            mean_cpu = mean(cpu),
            instances = n()) |> 
  mutate(across(where(is.numeric), round, digits = 2)) |> 
  DT::datatable() 
```



## Reduced generator - Summary tables

Below summary tables with summary results for different aggregation levels are given.

```{r}
dat_RGS <- read_csv(here::here("results/results_reduced_generator_sets_format.csv"))

# Note:
# - $RGS_size is the size of the reduced generator set (subset)
# - $RGS_sizes is the size of the minimum generator set (subset)
# - $RGS_size is the size of the minimum generator set (summed over subsets)

```



<!-- HER SKAL VI HAVE SUMMARY TABLES OPDELT PÅ LU|L, ... (SOM FIG 8 I ARTIKEL) -->

<!-- ### Strengthening the bounding set from above -->


```{r}
dat3 <- dat_RGS %>% filter(m != 3, other_equal) %>%
    select(
       filename,
       filename_levels,
       subproblem = subproblem_id,
       method = subset_global_method,
       lambda = partial_levels,
       gamma = other_partial_levels,
       q = q_stats_check,
       S = m,
       card_yns = Ys_sizes,
       card_gs = MGS_sizes,
       any_L_is_U, 
       other_all_L_is_U,
       L_is_U,
       other_partial_levels_factor
       # everything()
    ) |> 
    mutate(     
       q = q * 100,
       method = case_when(
          method == "m|m" ~ "$\\mM|\\mM$",
          method == "u|u" ~ "$\\mU|\\mU$",
          method == "ul|l" ~ "$\\mLU|\\mL$",
          method == "ul|u" ~ "$\\mLU|\\mU$",
          .default = "error"
       ),
       lb = case_when(
          any_L_is_U ~ "\\Yn^s",
          .default = "\\hull{\\Ynse^s}"
       )
    ) |> arrange(filename, filename_levels)
```




A summary table <!-- for Figure 8--> showing average relative number of redundant vectors ($q^m$), for different percentages of non-extreme nondominated vectors known (`lambda`), and different percentages of non-extreme nondominated vectors known of other subproblems (`gamma`).
      
```{r}

## upper bounds
# label functions
add_text_s <- function(string) paste0("$S=", string, "$")
add_text_g <- function(string) paste0("$\\gamma=", string, "$")


dat3 %>%
   mutate(card_yns = card_yns,
          card_gs = card_gs) %>%
   filter(card_yns != card_gs) %>%
   filter(!any_L_is_U) %>% 
   group_by(filename, lambda, gamma, S, method) |> 
   summarise(q = mean(q), n = n()) |> 
   arrange(gamma, S, lambda, method) |>
   group_by(S,lambda,method, gamma) |>
   summarise(avg_q = mean(q)) |>
   ungroup() |>
   pivot_wider(names_from =method, values_from=avg_q, values_fn = mean)  %>%
   mutate(
      #`$\\mLU|\\mL$` = round(`$\\mLU|\\mL$`,1),
      #`$\\mLU|\\mU$` = round(`$\\mLU|\\mU$`,1),
      #`$\\mLU|\\mU$` = round(`$\\mLU|\\mU$`,1),
      `$\\mLU|\\mL$` = round(`$\\mLU|\\mL$`,2),
      `$\\mLU|\\mU$` = round(`$\\mLU|\\mU$`,2),
      `$\\mM|\\mM$`   = round(`$\\mM|\\mM$`,2),
      `$\\mU|\\mU$`  = round(`$\\mU|\\mU$` ,2)
      ) %>%
   rename(
      #`$\\lambda$` = lambda,
      #`$\\gamma$` = gamma,
      #`$S$` = S,
      "LU|L" = `$\\mLU|\\mL$`,
      "LU|U" = `$\\mLU|\\mU$`,
      "M|M" = `$\\mM|\\mM$`,
      "U|U" = `$\\mU|\\mU$`
          ) %>%
   datatable()
# Render DataTable with LaTeX headers
   #datatable(escape = FALSE, options = list(
    # columnDefs = list(
    #   list(targets = 3, title = htmltools::HTML("$$\\lambda$$")),
    #   list(targets = 4, title = htmltools::HTML("$$\\gamma$$")),
    #   list(targets = 5, title = htmltools::HTML("$\\mLU|\\mL$$"))
    # )
   #))

```

A summary table for showing average relative number of redundant vectors ($q^m$), for each size $S \in \{2,4\}$ for different percentage of non-extreme nondominated vectors known (`lambda`).


```{r}
dat3 %>%
   mutate(card_yns = card_yns,
          card_gs = card_gs) %>%
   filter(card_yns != card_gs) %>%
   filter(!any_L_is_U) %>% 
   group_by(filename, lambda, gamma, S, method) |> 
   summarise(q = mean(q), n = n()) |> 
   arrange(gamma, S, lambda, method) |>
   group_by(S,lambda,method) |>
   summarise(avg_q = mean(q)) |>
   ungroup() |>
   pivot_wider(names_from =method, values_from=avg_q, values_fn = mean)  %>%
   mutate(
      `$\\mLU|\\mL$` = round(`$\\mLU|\\mL$`,2),
      `$\\mLU|\\mU$` = round(`$\\mLU|\\mU$`,2),
      `$\\mM|\\mM$`   = round(`$\\mM|\\mM$`,2),
      `$\\mU|\\mU$`  = round(`$\\mU|\\mU$` ,2)
      ) %>%
   rename(
      "LU|L" = `$\\mLU|\\mL$`,
      "LU|U" = `$\\mLU|\\mU$`,
      "M|M" = `$\\mM|\\mM$`,
      "U|U" = `$\\mU|\\mU$`
          ) %>%
   datatable()
```


<!-- A summary table of figure 9 -->

<!-- ### Strengthening the bounding set from below -->

A summary table <!--of Figure 9--> showing average relative number of redundant vectors ($q^m$), for each size $S \in \{2,4\}$ for different percentage of non-extreme nondominated vectors known (`lambda`), and for different lower bound sets ${L}^s = \text{conv}({Y}^s_\mathtt{SE})$ (`CONV`) and ${L}^s = {Y}^s_\mathtt{N}$ (`ALL`).

```{r, eval=FALSE} 
# Figure 9
## lower bounds
add_text_lb <- function(string) paste0("$\\L^s=", string, "$")

dat3 %>% filter(card_yns != card_gs) %>%
   filter(!(any_L_is_U & !other_all_L_is_U)) %>%
   filter(L_is_U == FALSE) %>%
   filter(card_yns != card_gs) %>% 
   filter(other_partial_levels_factor %in% c("100",'all')) %>% 
   group_by(filename, lambda, S, method, lb) |>
   summarise(q = mean(q), n = n()) |>
   arrange(S, lambda, method) |>
   ggplot(aes(x = lambda, y = q, color = method)) +
   geom_point(size = 0.7, alpha = 0.5) +
   stat_summary(fun = mean, geom = "line", alpha = 0.7) +
   facet_grid(S ~ lb, labeller = labeller(S = add_text_s, lb = add_text_lb)) +
   labs(
      y = "Average relative number of redundant vectors ($q^m$)",
      x = "Percentage of non-extreme nondominated vectors known ($\\lambda$)", 
      color = NULL
   ) +
   scale_linetype_manual(values = c("solid", "dashed", "dotted", "dotdash")) +
   scale_y_continuous(labels = scales::number_format(big.mark = ",", prefix = "\\ "), breaks = seq(0, 100, by = 25)) +
   # guides(color = guide_legend(override.aes = list(linetype = 0, keywidth = 16))) +
   theme_bw() +
   theme(
      axis.title.y = element_text(vjust = 3),
      axis.title.x = element_text(vjust = -3),
      legend.position = "bottom", legend.key.width = unit(1, "cm"))  # legend.key.width = unit(2, "cm")
```


```{r}

## lower bounds
add_text_lb <- function(string) paste0("$\\L^s=", string, "$")

dat3 %>% filter(card_yns != card_gs) %>%
   filter(!(any_L_is_U & !other_all_L_is_U)) %>%
   filter(L_is_U == FALSE) %>%
   filter(card_yns != card_gs) %>% 
   filter(other_partial_levels_factor %in% c("100",'all')) %>% 
   group_by(filename, lambda, S, method, lb) |>
   summarise(q = mean(q), n = n()) |>
   arrange(S, lambda, method) |>
   group_by(S,method, lambda,lb) %>% 
      summarise(avg_q = mean(q)) |>
   ungroup() |>
   pivot_wider(names_from =method, values_from=avg_q, values_fn = mean)  %>%
   mutate(
      `$\\mLU|\\mL$` = round(`$\\mLU|\\mL$`,2),
      `$\\mLU|\\mU$` = round(`$\\mLU|\\mU$`,2),
      `$\\mM|\\mM$`   = round(`$\\mM|\\mM$`,2),
      `$\\mU|\\mU$`  = round(`$\\mU|\\mU$` ,2)
      ) %>%
   rename(
      "LU|L" = `$\\mLU|\\mL$`,
      "LU|U" = `$\\mLU|\\mU$`,
      "M|M" = `$\\mM|\\mM$`,
      "U|U" = `$\\mU|\\mU$`
          ) %>%
    mutate( lb = case_when(
       lb == "\\Yn^s" ~ "ALL",
       .default = "CONV"
    ),) %>% 
   datatable()

```


<!-- HEREFTER SUMMARY TAB FOR INSTANCS, S, SPCARD ETC. -->

A summary table showing the average relative number of redundant vectors ($q^m$) `avg_q`, average minimum generator set sizes `avg_MGS_size` and average reduced generator set sizes ´avg_RGS_size´ for each $S \in \{2,4\}$, for different subproblem sizes `sp_card` $|{Y}^s_\mathtt{N}| \in \{50,100,200,300\}$. The cases with no redundant ND vectors are filtered out. 

```{r}
dat_RGS %>% 
  filter(other_equal == TRUE) %>% 
  filter(m!= 3) %>% 
  filter(!(any_L_is_U & !other_all_L_is_U)) %>% 
  filter(L_is_U == FALSE) %>% 
  filter(Ys_sizes != MGS_sizes) %>% 
  group_by(
     S = m,
     sp_card = Ys_sizes,
     subset_method = toupper(subset_method),
     # other_partial_levels_factor,
     # partial_levels_factor
     ) %>%
  summarise(avg_q = mean(q_stats_check),avg_MGS_size = round(mean(MGS_sizes),1), avg_RGS_size = round(mean(RGS_size),1)) %>% 
  mutate(avg_q = percent(avg_q,decimals)) %>%
  rename(method = subset_method) %>% 
  DT::datatable() 
```

